Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-11-29 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
unifying tables for experiments

\begin{enumerate}[label=]
\fontsize{9pt}{10pt}
\item \textbf{F1}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest \}}
\item \textbf{F2}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT \}}
\item \textbf{F3}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, EST \}} 
\item \textbf{F4}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, ML \}} 
\item \textbf{F5}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT, EST \}}
\item \textbf{F6}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT, ML \}} 
\item \textbf{F7}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, EST, ML \}}
\item  \textbf{F8}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT, EST, ML \}}
\item \textbf{F9}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest \}} 
\item \textbf{F10}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT \}} 
\item \textbf{F11} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, EST \}} 
\item \textbf{F12} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, ML \}}
\item \textbf{F13} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, EST \}}
\item \textbf{F14} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, ML \}}
\item \textbf{F15} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, EST, ML \}}
\item \textbf{F16} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, EST, ML \}}
\end{enumerate}

\begin{table}[bt]
  \begin{center}
    \caption{Solution quality comparison for different sets of features (Taillard's instances).}
    \label{tab4}
    \addtolength{\tabcolsep}{1pt}
    \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|} \hline
%      & \multicolumn{11}{|c|}{\textbf{Instances}} \\ \cline{2-12}
      \textbf{Approach}   & TA51                           & TA52                           & TA53                           & TA54 & TA55                           & TA56                           & TA57                           & TA58 & TA59                           & TA60 & AVG  \\ \hline\hline
      \textbf{FIFO}        & 3549                           & 3339                           & \textbf{3160}              & \textbf{3218} & 3291               & 3325                           & 3654                           & \textbf{3299} & \textbf{3344}                           & \textbf{3129} & \textbf{3331} \\
      \textbf{MTWR}        & \textbf{3364}           & \textbf{3304}              & 3168                           & 3494 & \textbf{3237}                           & \textbf{3287}               & \textbf{3633}              & 3591 & 3394                           & 3257 & 3373 \\
      \textbf{Single-shot} & 3632                           & 3615                           & 3481                           & 3462 & 3552                           & 3610                           & 3778                           & 3718 & 3613                           & 3550 & 3601 \\ % \hline
%      \textbf{EST}         
      \textbf{Multi-shot}         & 3506                           & 3773                           & 3478                           & 3497 & 3482                           & 3605                           & 3753                           & 3731 & 3398                           & 3247 & 3547 \\ \hline
      \textbf{F1}          & 3506                           & 3277                           & 3382                           & 3414 & 3308                           & 3353                           & 3605                           & 3352 & 3453                           & 3483 & 3413 \\
      \textbf{F2}          & 3362                           & 3318                           & 3585                           & 3425 & 3441                           & 3380                           & 3573                           & 3412 & 3416                           & \textbf{3315} & 3423 \\
      \textbf{F3}          & 3324                           & 3330                           & 3347                           & 3425 & 3424                           & 3548                           & 3601                           & 3370 & 3301                           & 3617 & 3429 \\
      \textbf{F4}          & 3360                           & 3286                           & 3543                           & 3503 & 3319                           & 3270                           & 3583                           & 3509 & 3339                           & 3563 & 3428 \\
      \textbf{F5}          & 3346                           & 3243                           & 3517                           & 3397 & 3355                           & 3383                           & 3650                           & 3707 & 3508                           & 3591 & 3470 \\
      \textbf{F6}          & \textbf{3294} & 3275                           & 3250                           & 3265 & 3386                           & 3366                           & \textbf{3480} & \textbf{3324} & 3430                           & 3327 & \textbf{3340} \\
      \textbf{F7}          & 3328                           & 3226                           & 3338                           & 3353 & 3301                           & 3564                           & 3592                           & 3496 & 3352                           & 3399 & 3395 \\

@@

The resulting quality of schedules in terms of the achieved makespan for each instance is reported in Table~\ref{tab4} and Table~\ref{tab5},
where the first four rows include the greedy FIFO and MTWR search methods supplied by the environment in~\cite{tagesc21a}
as well as single-shot and multi-shot pure ASP optimization, the latter taking earliest starting times instead of 
clustering for the decomposition into $3$ time windows,
for reference.
\begin{table}[bt]
  \begin{center}
    \caption{Solution quality comparison for different sets of features (Demirkol's instances).}
    \label{tab5}

    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|} \hline
      & \multicolumn{11}{|c|}{\textbf{Instances}} \\ \cline{2-12}
      \textbf{Approach}  & Dmu31  & Dmu32 & Dmu33 & Dmu34 & Dmu35 & Dmu71 & Dmu72 & Dmu73 & Dmu74 & Dmu75 & AVG  \\ \hline

      \textbf{FIFO}  & \textbf{6817} & \textbf{6318} & \textbf{6029} & \textbf{6395} & \textbf{6409} & 9678 & 10349 & 9617 & 9847 & 9479 & 8094 \\
      \textbf{MTWR}  & 7155 & 6042 & 6819 & 6570 & 6881 & 7764 & 8407 & 8411 & 8321 & 7893 & \textbf{7426} \\
      \textbf{Single-shot} & 10370 & 10214 & 10064 & 10682 & 10203 & 6848 & 28369 & 32954 & 35325 & 6992 & 16202 \\
      \textbf{EST} & 10318  & 9522  & 9785 & 10775 & 10398 & \textbf{6492}  & \textbf{6935} & \textbf{7202} & \textbf{7128}  & \textbf{6243} & 8480 \\ \hline
      \textbf{F1}  & 8488  & 8325  & 7831 & 8356 & 8088 & 8593  & 7188 & 7826 & 6611 & 7662 & 7897 \\
      \textbf{F2}  & 8440  & 8298  & \textbf{7663} & 8479 & 7986 & 6994  & 7606 & 7209 & 6627 & 7069 & 7637 \\
      \textbf{F3}  & 8234  & 8401  & 8037 & 8444 & 7780 & \textbf{6590}  & 7785 & 7302 & 6690 & 7051 & 7631 \\
      \textbf{F4}  & 7991  & 8589  & 7996 & 8471 & 8207 & 8091  & 7834 & 6972 & 6708 & 6859 & 7771 \\
      \textbf{F5}  & 8164  & 8103  & 7835 & 8482 & 7802 & 6807  & 8357 & 7328 & 6774 & 7192 & 7684\\
      \textbf{F6}  & \textbf{7709} & 8265 & 7795 & 8475 & \textbf{7678}  & 6611 & 6708 & 7030 &6569 & 6867 & \textbf{7371} \\
      \textbf{F7}  & 8268  & 8553  & 7892 & 8359 & 8032 & 7603  & 6855 & 7223 & 6609 & 7200 & 7659 \\
      \textbf{F8}  & 8873 & 8879 & 8201 & 9126 & 7982 & 6843 & 7971 & 7106 & 7545 & 6970 & 7950 \\
      \textbf{F9}  & 8500  & 8185  & 8533 & 8772 & 8535 & 6726 & 6518& 7130 & 6592 & 7262 & 7675 \\
      \textbf{F10}  & 8322  & 8119  & 8433 & 8910 & 8233 & 6868 & 6764 & 7183 & 6267 & 7459 & 7656 \\
      \textbf{F11} & 8617  & 8383  & 8614 & 8755 & 7969 & 7587 & \textbf{6512} & \textbf{6762}& 6505 & 7376 & 7708 \\
      \textbf{F12} & 8400  & 8124  & 8043 & \textbf{8185} & 8799 & 7849 & 6618 & 6876 & 6397 & 7746 & 7704 \\
      \textbf{F13} & 8916 & 8343  & 8441 & 8331 & 8153 & 7464 & 6757 & 6994 & 6434 & 6961 & 7679 \\
      \textbf{F14} & 8392  & \textbf{7937} & 7943 & 8375 & 8049 & 7310 & 7703 & 6827 & \textbf{6126} & 6893 & 7555 \\
      \textbf{F15} & 8412  & 8210  & 8117 & 8563 & 9068 & 7853 & 6968 & 6909 & 6350  & 7011 & 7746 \\
      \textbf{F16} & 8184 & 8150 & 8295 & 8721 & 8003 & 6997 & 7156 & 6991 & 6355 & \textbf{6584} & 7544 \\ 
      \textbf{Virtual Best} & \textbf{6817} & \textbf{6318} & \textbf{6029} & \textbf{6395} & \textbf{6409} & \textbf{6492} & \textbf{6512} & \textbf{6762} & \textbf{6126} & \textbf{6243} & \textbf{6410} \\
\hline
      \end{tabular}
  \end{center}
\end{table}

>>>>

\begin{enumerate}[label=]
\fontsize{9pt}{10pt}
\item \textbf{F1}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest \}}
\item \textbf{F2}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT \}}
\item \textbf{F3}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, EST \}} 
\item \textbf{F4}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, ML \}} 
\item \textbf{F5}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT, EST \}}
\item \textbf{F6}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT, ML \}} 
\item \textbf{F7}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, EST, ML \}}
\item  \textbf{F8}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT, EST, ML \}}
\item \textbf{F9}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest \}} 
\item \textbf{F10} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT \}} 
\item \textbf{F11} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, EST \}} 
\item \textbf{F12} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, ML \}}
\item \textbf{F13} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, EST \}}
\item \textbf{F14} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, ML \}}
\item \textbf{F15} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, EST, ML \}}
\item \textbf{F16} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, EST, ML \}}
\end{enumerate}

\begin{table}[bt]
  \begin{center}
    \caption{Solution quality comparison for different feature sets (Taillard's instances).}
    \label{tab4}
    \addtolength{\tabcolsep}{0.9pt}
    \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|} \hline
%      & \multicolumn{11}{|c|}{\textbf{Instances}} \\ \cline{2-12}
      \textbf{Approach}   & TA51                           & TA52                           & TA53                           & TA54 & TA55                           & TA56                           & TA57                           & TA58 & TA59                           & TA60 & AVG  \\ \hline\hline
      \textbf{FIFO}        & 3549                           & 3339                           & \textbf{3160}              & \textbf{3218} & 3291               & 3325                           & 3654                           & \textbf{3299} & \textbf{3344}                           & \textbf{3129} & \textbf{3331} \\
      \textbf{MTWR}        & \textbf{3364}           & \textbf{3304}              & 3168                           & 3494 & \textbf{3237}                           & \textbf{3287}               & \textbf{3633}              & 3591 & 3394                           & 3257 & 3373 \\
      \textbf{Single-shot} & 3632                           & 3615                           & 3481                           & 3462 & 3552                           & 3610                           & 3778                           & 3718 & 3613                           & 3550 & 3601 \\ % \hline
%      \textbf{EST}         
      \textbf{Multi-shot}         & 3506                           & 3773                           & 3478                           & 3497 & 3482                           & 3605                           & 3753                           & 3731 & 3398                           & 3247 & 3547 \\ \hline
      \textbf{F1}          & 3506                           & 3277                           & 3382                           & 3414 & 3308                           & 3353                           & 3605                           & 3352 & 3453                           & 3483 & 3413 \\
      \textbf{F2}          & 3362                           & 3318                           & 3585                           & 3425 & 3441                           & 3380                           & 3573                           & 3412 & 3416                           & \textbf{3315} & 3423 \\
      \textbf{F3}          & 3324                           & 3330                           & 3347                           & 3425 & 3424                           & 3548                           & 3601                           & 3370 & 3301                           & 3617 & 3429 \\
      \textbf{F4}          & 3360                           & 3286                           & 3543                           & 3503 & 3319                           & 3270                           & 3583                           & 3509 & 3339                           & 3563 & 3428 \\
      \textbf{F5}          & 3346                           & 3243                           & 3517                           & 3397 & 3355                           & 3383                           & 3650                           & 3707 & 3508                           & 3591 & 3470 \\
      \textbf{F6}          & \textbf{3294} & 3275                           & 3250                           & 3265 & 3386                           & 3366                           & \textbf{3480} & \textbf{3324} & 3430                           & 3327 & \textbf{3340} \\
      \textbf{F7}          & 3328                           & 3226                           & 3338                           & 3353 & 3301                           & 3564                           & 3592                           & 3496 & 3352                           & 3399 & 3395 \\

@@

The resulting quality of schedules in terms of the achieved makespan for each instance is reported in Table~\ref{tab4} and Table~\ref{tab5},
where the first four rows include the greedy FIFO and MTWR search methods supplied by the environment in~\cite{tagesc21a}
as well as single-shot and multi-shot pure ASP optimization, the latter taking earliest starting times instead of 
clustering for the decomposition into $3$ time windows,
for reference.
\begin{table}[bt]
  \begin{center}
    \caption{Solution quality comparison for different feature sets (Demirkol's instances).}
    \label{tab5}
    \addtolength{\tabcolsep}{0.9pt}
    \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|} \hline
%      & \multicolumn{11}{|c|}{\textbf{Instances}} \\ \cline{2-12}
      \textbf{Approach}  & DE31  & DE32 & DE33 & DE34 & DE35 & DE71 & DE72 & DE73 & DE74 & DE75 & AVG  \\ \hline

      \textbf{FIFO}  & \textbf{6817} & 6318 & \textbf{6029} & \textbf{6395} & \textbf{6409} & 9678 & 10349 & 9617 & 9847 & 9479 & 8094 \\
      \textbf{MTWR}  & 7155 & \textbf{6042} & 6819 & 6570 & 6881 & 7764 & 8407 & 8411 & 8321 & 7893 & \textbf{7426} \\
      \textbf{Single-shot} & 10370 & 10214 & 10064 & 10682 & 10203 & 6848 & 28369 & 32954 & 35325 & 6992 & 16202 \\
      \textbf{Multi-shot} & 10318  & 9522  & 9785 & 10775 & 10398 & \textbf{6492}  & \textbf{6935} & \textbf{7202} & \textbf{7128}  & \textbf{6243} & 8480 \\ \hline
      \textbf{F1}  & 8488  & 8325  & 7831 & 8356 & 8088 & 8593  & 7188 & 7826 & 6611 & 7662 & 7897 \\
      \textbf{F2}  & 8440  & 8298  & \textbf{7663} & 8479 & 7986 & 6994  & 7606 & 7209 & 6627 & 7069 & 7637 \\
      \textbf{F3}  & 8234  & 8401  & 8037 & 8444 & 7780 & \textbf{6590}  & 7785 & 7302 & 6690 & 7051 & 7631 \\
      \textbf{F4}  & 7991  & 8589  & 7996 & 8471 & 8207 & 8091  & 7834 & 6972 & 6708 & 6859 & 7771 \\
      \textbf{F5}  & 8164  & 8103  & 7835 & 8482 & 7802 & 6807  & 8357 & 7328 & 6774 & 7192 & 7684\\
      \textbf{F6}  & \textbf{7709} & 8265 & 7795 & 8475 & \textbf{7678}  & 6611 & 6708 & 7030 &6569 & 6867 & \textbf{7371} \\
      \textbf{F7}  & 8268  & 8553  & 7892 & 8359 & 8032 & 7603  & 6855 & 7223 & 6609 & 7200 & 7659 \\
      \textbf{F8}  & 8873 & 8879 & 8201 & 9126 & 7982 & 6843 & 7971 & 7106 & 7545 & 6970 & 7950 \\
      \textbf{F9}  & 8500  & 8185  & 8533 & 8772 & 8535 & 6726 & 6518& 7130 & 6592 & 7262 & 7675 \\
      \textbf{F10}  & 8322  & 8119  & 8433 & 8910 & 8233 & 6868 & 6764 & 7183 & 6267 & 7459 & 7656 \\
      \textbf{F11} & 8617  & 8383  & 8614 & 8755 & 7969 & 7587 & \textbf{6512} & \textbf{6762}& 6505 & 7376 & 7708 \\
      \textbf{F12} & 8400  & 8124  & 8043 & \textbf{8185} & 8799 & 7849 & 6618 & 6876 & 6397 & 7746 & 7704 \\
      \textbf{F13} & 8916 & 8343  & 8441 & 8331 & 8153 & 7464 & 6757 & 6994 & 6434 & 6961 & 7679 \\
      \textbf{F14} & 8392  & \textbf{7937} & 7943 & 8375 & 8049 & 7310 & 7703 & 6827 & \textbf{6126} & 6893 & 7555 \\
      \textbf{F15} & 8412  & 8210  & 8117 & 8563 & 9068 & 7853 & 6968 & 6909 & 6350  & 7011 & 7746 \\
      \textbf{F16} & 8184 & 8150 & 8295 & 8721 & 8003 & 6997 & 7156 & 6991 & 6355 & \textbf{6584} & 7544 \\ 
      \textbf{Virtual Best} & \textbf{7709} & \textbf{7937} & \textbf{7663} & \textbf{8185} & \textbf{7678} & \textbf{6590} & \textbf{6512} & \textbf{6762} & \textbf{6126} & \textbf{6584} & \textbf{7175} \\
\hline
      \end{tabular}
  \end{center}
\end{table}
